Facotrs Influence Stress in Canada

### 2022-03-19 outputs/paper/paper.Rmd
final commit

---
title: ' 304 paper 3 '
author:
- Zihan Zhang
- Qiuhan Wang
thanks: "Code and data are available at: https://github.com/zihanjasmine/Toronto-shelter-flow."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "More and more Canadian social and economic issues have led to many discussions about stress levels. Assessing people’s mental health is beneficial for the government to take actions to improve people’s happiness index. In the report, we use the “Canadians at Work and Home” aspect of 2016 Canadian Government General Social Survey data to analyze factors influencing Canadian stress levels. The results of the survey suggest that job satisfactions, living standards, sex and many other factors play big roles in stress assessments. Moreover, 39.4% of people feel not stressed and 43.2% of people feel a bit stressed in Canada, which means that government can take more actions to help people balance their lifestyle, work, and well-being."
output:
  bookdown::pdf_document2
bibliography: references.bib'
---

@@

@@

## Introduction

@@

A short survey was created and conducted in 2016 to assess the mental health of all persons who are equal to or larger than 15 years old in 10 provinces in Canada. To ensure proper stratification and geographic distribution, our sample population be reached via letter. The letters are sent to the households which include purpose and access code to login in survey applicants. In order to decrease the non-respond rate, the survey is conducted online and via telephone. From the response, most of responders feel not very stressful or a little bit stressful. To be more specific, pressure of mainly comes from work, while pressure of females mainly comes from family. The number of children in households influences people’s stress level as well. The logistic model displays that standard living and personal relationship are other two large factors to influence stress level.

From our survey responses, some limitations and survey response biases were observed. For the sample population, we found that some homeless people cannot be connected via mail or telephone, but they are included in the target population. Also, this kind of person is more likely to have a lower health rate assessment because of poor quality of life. It might influence the result of the survey. Also, using computer-assisted telephone interviews may bring some non-sampling errors. In detail, interviewers may have some technical problems or misunderstand instructions. From GSS, some questionnaires suggested ambitious answer such as rating job satisfactions, because responders may self-rate themselves with the different standards. Therefore, a further survey must be operated in order to group the people under high mental pressure.

The article is structured as follows. First, I introduce the survey including the survey method and detailed questionnaires relating to mental health. Second, some important variables such as sex, satisfaction with work, life habits are collected, in order to analyze what kind of group bears greater mental pressure. Finally, the supplementary survey is provided to get more information about the target group and increase the accuracy of the data.

## Data

### Data collection

@@

###Data processing

@@

### Population and sample

The GSS survey collected 19,609 questionnaires. The target population is non-institutionalized individuals aged over 15 years old in 10 Canadian provinces. 
In this paper, we selected only some of the useful variables related to mental health in the survey and eliminated invalid responses. Therefore, our data is reduced and it contains 16440 observations. Since we have a large amount of data, removing some observations will not lead to a significant impact on the conclusions drawn from the data.

### Survey method

@@

Non-sampling errors may occur at survey operation, especially in the CATI phase. In detail, using CATI, interviewers may misunderstand instructions and respondents may make errors in answering questions. Therefore, the results of the survey may be inaccurately recorded in the system so that the errors may be viewed in the final data. To combat this factor, many measures were used to promise the quality of data and reduce the non-sampling errors at the data collecting step. These measures included the use of highly skilled interviewer’s judging respondents’ answers accurately, training of interviewers focused on questionnaire and observation of interviewers’ misunderstanding of instructions.

## Result

Moreover, we can see that almost half of the sampling population works 40 hours per week, and nearly a quarter of people has to work overtime to complete their job from figure \@ref(fig:hours). From table  \@ref(tab:tablestress) and figure \@ref(fig:piegraph), we can tell that Canadian people generally have lower stress levels and work and family are the main sources of stress in life. 80% of Canadians feel a little stress in life. Work stress accounts for the largest share of stress, which is 23%. If we look into the details of the graphs, we find that there is a big difference in the sources of stress for men and women. 26% of women cite family as their primary source of stress, twice as many as men. 32% of males consider work as their main source of stress, while that of female is 18%. We can tell from the graphs that women take more responsibility for child care, housework, while men are the main breadwinners.

library(modelsummary)

@@

```{r satisfaction,warning=FALSE,message=FALSE,echo = FALSE}
ggplot(clean_data, 
       aes(x = stress, 
           fill = factor(job_satisfication))) + 
geom_bar(position = "dodge") +
labs(x="stress level",
     fill="Job satisfaction",
     title="Job satisfaction and stress level")

@@

Based on our findings above, we build a linear regression model to estimate Canadian's stress level. From table \@ref(tab:regression), older people with higher job satisfaction  health level has higher stress level. Appearance level and personal relationship level has weak correlation with stress. However, our model has a low R-Squared value, which suggests that our model shows a low correlation.

## Discussion

### Purpose and summary for the survey

@@

### Learn about the world

@@

To the people who feel stressful because of their health condition, the companies where they work for can provide physical examination to them. The physical examination can help people assess their health status, so some potential illness can be discovered as early as possible. The government can give more subsidies to people with serious disease in order to help them be recovery.

### Weakness and areas in the future

Our survey method contains some limitations and the survey method can be improved by some approaches. First, in the survey, we only select one of the members in a household which means that the member who be selected cannot represents other household members’ opinions. It may influence the accuracy of the result. Therefore, selecting more members in a household may be a better way to collect data. Second, the government statistic department connects with respondents via mail or telephone. This process may ignore the group of people who cannot connect with these two approaches, such as the homeless. However, the responses from this group are valuable to our research, because this particular group of people is more likely to suffer from stress. The homeless’ job satisfaction, unfair treatment/discrimination, participation in outdoor activities, and other variables may be different with existing respondents’. The homeless’ living habits including alcohol consumption and smoking frequency may need to be further investigated. In the future survey, we suggest adding a new approach in-person questionnaire to collect data so that the homeless group can be contained.

Some non-sampling errors occur in the survey as well. Using CATI to collect data, interviewers may misunderstand instructions and respondents especially the olds may make errors in answering questions. Therefore, the results of the survey may be inaccurately recorded in the system so that the errors may be viewed in the final data. To combat this factor and promise the quality of data, some technical measures should be considered. These measures included the use of highly skilled interviewers judging respondents’ answers accurately, training of interviewers focused on the questionnaire, and observation of interviewers’ misunderstanding of instructions.

In addition, some questions in the survey are ambiguous which may influence the result of the survey. To be more specific, everyone has his standards to estimate his job satisfaction from 1 to 10 so that we cannot unitize the results. Also, some responders cannot identify their stress level because it’s so abstract. Therefore, we do an additional questionnaire to help responders rate themselves. For example, we add questions “How often have you been bothered by poor appetite?” and “How often do you feel depressed?” to describe details of stress. Similar ambiguous self-rating questions appearing in job satisfaction and other variables, we suggest to use more specific questions to instead as well.

Finally, we should do more researches to describe the impacts of stress. When people are fully aware of the high-stress level’s harm to their health condition and mental condition, they would pay attention to deal with pressure. The social problem, like “How to balance life, work and well-being” can raise concern.

# survey question

### Survey introduction

@@

I am writing to invite you to participate in this research by completing the questionnaire. This survey aims to study various factors that make Canadians feel stressed. The following questionnaire contains a few multiple-choice questions and it will take approximately 5 minutes. All data collected will be kept confidential by the government of Canada. An extensive disclosure risk analysis is conducted before releasing the data to ensure that the data does not reveal personal information. Individual responses are not shared.
Thanks for your corporation.

Sincerely,
On behalf of the government of Canada

@@

# Reference

1.Candian GSS
Government of Canada, S. C. (2017, February 27). The General Social Survey: An overview. Government of Canada, Statistics Canada. Retrieved March 8, 2022, from https://www150.statcan.gc.ca/n1/pub/89f0115x/89f0115x2013001-eng.htm

2.R
 R Core Team (2021). R: A language and environment for statistical computing. R
  Foundation for Statistical Computing, Vienna, Austria. URL
  https://www.R-project.org/.

3. ggplot2
 H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New
  York, 2016.

4. modelsummary

@@

>>>>

---
title: "Facotrs Influence Stress in Canada"
author:
- Zihan Zhang
- Qiuhan Wang
thanks: "Code and data are available at: https://github.com/zihanjasmine/Factors-influence-stress-in-Canada."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "More and more Canadian social and economic issues have led to many discussions about stress levels. Assessing people’s mental health is beneficial for the government to take actions to improve people’s happiness index. In the report, we use the “Canadians at Work and Home” aspect of 2016 Canadian Government General Social Survey data to analyze factors influencing Canadian stress levels. The results of the survey suggest that job satisfactions, living standards, sex and many other factors play big roles in stress assessments. Moreover, 39.4% of people feel not stressed and 43.2% of people feel a bit stressed in Canada, which means that government can take more actions to help people balance their lifestyle, work, and well-being."
output:
  bookdown::pdf_document2
bibliography: references.bib
---

@@

clean_data <- clean_data %>%
  mutate(gender = case_when(sex == '1'~ "Male",
                            TRUE ~ "Female"))

@@

\newpage
# Introduction

@@

Workload and working environment are two factors influencing people's stress levels, which were discussed in the book "Are Quebecers More Stressed Out at Work Than Other" by the University of Ottawa Department of Economics in 2016. We already know the standard of living and health conditions will affect people's stress level in the UK, maybe not in Canada so we want to see how the variables affect Canadians(Hulst et al., 2014). There are variables such as alcohol consumption and smoking frequency potentially affect stress level but weren't investigated before.

A short survey was created and conducted in 2016 to assess the mental health of all persons who are equal to or larger than 15 years old in 10 provinces in Canada. To ensure proper stratification and geographic distribution, our sample population be reached via letter. The letters are sent to the households which include purpose and access code to login in survey applicants. In order to decrease the non-respond rate, the survey is conducted online and via telephone. From the response, most of the respondents feel not very stressful or a little bit stressful. To be more specific, the pressure mainly comes from work, while the pressure of females mainly comes from family. The number of children in households influences people’s stress levels as well. The logistic model displays that standard living and personal relationships are other two large factors to influence stress levels.

The article is structured as follows. First, we introduce the survey including the survey method and detailed questionnaires relating to mental health. Second, some important variables such as sex, satisfaction with work, life habits are collected, in order to analyze what kind of group bears greater mental pressure. Finally, the supplementary survey is provided to get more information about the target group and increase the accuracy of the data.

# Data

## Data collection

@@

## Data processing

@@

## Population and sample

The GSS survey collected 19,609 questionnaires. The target population is non-institutionalized individuals aged over 15 years old in 10 Canadian provinces. 
In this paper, we selected only some of the useful variables related to mental health in the survey and eliminated invalid responses. Therefore, our data is reduced and it contains 16440 observations. Since we have a large amount of data, removing some observations will not lead to a significant impact on the conclusions drawn from the data. We selected 16 variables such as gender, age, and job satisfaction that we thought would have an impact on the stress situation. In our analysis, we consider stress level as our response variable.

Here we show an extract of our dataset.(Table \@ref(tab:tablestress))

## Survey method

@@

Non-sampling errors may occur at survey operation, especially in the CATI phase. In detail, using CATI, interviewers may misunderstand instructions and respondents may make errors in answering questions. Therefore, the results of the survey may be inaccurately recorded in the system so that the errors may be viewed in the final data. To combat this factor, many measures were used to promise the quality of data and reduce the non-sampling errors at the data collecting step. These measures included the use of highly skilled interviewer’s judging respondents’ answers accurately, training of interviewers focused on the questionnaire and observation of interviewers’ misunderstanding of instructions.

# Result

@@

```{r satisfaction,warning=FALSE,message=FALSE,echo = FALSE}
ggplot(clean_data, 
       aes(x = stress, 
           fill = factor(job_satisfaction))) + 
geom_bar(position = "dodge") +
labs(x="stress level",
     fill="Job satisfaction",
     title="Job satisfaction and stress level")

@@

We can see that almost half of the sampling population works 40 hours per week, and nearly a quarter of people has to work overtime to complete their job from figure \@ref(fig:hours). Constantly working long hours might lead to fatigue,  lower performance level of employees and lack of free time etc.-all of which makes employees feel overwhelmed and high level of stress. From table  \@ref(tab:tablestress) and figure \@ref(fig:piegraph), we can tell that Canadian people generally have lower stress levels and work and family are the main sources of stress in life. 80% of Canadians feel a little stress in life. Work stress accounts for the largest share of stress, which is 23%. If we look into the details of the graphs, we find that there is a big difference in the sources of stress for men and women. 26% of women cite family as their primary source of stress, twice as many as men. 32% of males consider work as their main source of stress, while that of female is 18%. We can tell from the graphs that women take more responsibility for child care, housework, while men are the main breadwinners.

Based on our findings above, we build a linear regression model to estimate Canadian's stress level. From table \@ref(tab:regression), older people with lower job satisfaction and lower health level has higher stress level. Appearance level and personal relationship level has weak correlation with stress. However, our model has a low R-Squared value, which suggests that the goodness of fitting is not ideal.

# Discussion

## Purpose and summary for the survey

@@

## Learn about the world

@@

To the people who feel stressful because of their health condition, the companies where they work can provide physical examinations to them. A physical examination can help people assess their health status, so some potential illnesses can be discovered as early as possible. The government can give more subsidies to people with serious diseases in order to help them recover.

## Weakness and areas in the future

Our survey method contains some limitations and the survey method can be improved by some approaches. First, in the survey, we only select one of the members in a household which means that the member who is selected cannot represent other household members’ opinions. It may influence the accuracy of the result. Therefore, selecting more members in a household may be a better way to collect data. Second, the government statistic department connects with respondents via mail or telephone. This process may ignore the group of people who cannot connect with these two approaches, such as the homeless. However, the responses from this group are valuable to our research, because this particular group of people is more likely to suffer from stress. The homeless’ job satisfaction, unfair treatment/discrimination, participation in outdoor activities, and other variables may be different from existing respondents’. The homeless’ living habits including alcohol consumption and smoking frequency may need to be further investigated. In the future survey, we suggest adding a new approach in-person questionnaire to collect data so that the homeless group can be contained.

Some non-sampling errors occur in the survey as well. Using CATI to collect data, interviewers may misunderstand instructions, and respondents, especially the olds may make errors in answering questions. Therefore, the results of the survey may be inaccurately recorded in the system so that the errors may be viewed in the final data. To combat this factor and promise the quality of data, some technical measures should be considered. These measures included the use of highly skilled interviewers judging respondents’ answers accurately, training of interviewers focused on the questionnaire, and observation of interviewers’ misunderstanding of instructions.

In addition, some questions in the survey are ambiguous which may influence the result of the survey. To be more specific, everyone has his standards to estimate his job satisfaction from 1 to 10 so that we cannot unitize the results. Also, some responders cannot identify their stress level because it’s so abstract. Therefore, we do an additional questionnaire to help responders rate themselves. For example, we add questions “How often have you been bothered by poor appetite?” and “How often do you feel depressed?” to describe details of stress. Similar ambiguous self-rating questions appearing in job satisfaction and other variables, we suggest using more specific questions instead as well.

Our model has a low R-Squared value when we use the regression model to analyze the relationship among sex, stress level, health level, personal relationship level, number of children, and appearance level. Low R-squared value displays that the goodness of fitting is not ideal. Therefore, we need to select the more related variable in further investigation.

Finally, we should do more research to describe the impacts of stress. When people are fully aware of the harm of high-stress levels to their health condition and mental condition, they would pay attention to deal with pressure. The social problem, like “How to balance life, work and well-being”, can raise concern.

\newpage
# Supplementary survey

## Survey introduction

@@

I am writing to invite you to participate in this research by completing the following questionnaire. This survey aims to study various factors that make Canadians feel stressed. The following questionnaire contains a few multiple-choice questions and it will take approximately 5 minutes. All data collected will be kept confidential by the government of Canada. An extensive disclosure risk analysis is conducted before releasing the data to ensure that the data does not reveal personal information. Individual responses are not shared.

Thanks for your corporation.

Sincerely,

On behalf of the government of Canada

## Queationnaire

@@

```{r,echo=FALSE, fig.align='center', out.width = '80%'}
knitr::include_graphics("Questionnaire1.png")
```

```{r,echo=FALSE, fig.align='center', out.width = '80%'}
knitr::include_graphics("Questionnaire2.png")
```

```{r,echo=FALSE, fig.align='center', out.width = '80%'}
knitr::include_graphics("Questionnaire3.png")
```

```{r,echo=FALSE, fig.align='center', out.width = '80%'}
knitr::include_graphics("Questionnaire4.png")
```

```{r,echo=FALSE, fig.align='center', out.width = '80%'}
knitr::include_graphics("Questionnaire5.png")
```

```{r,echo=FALSE, fig.align='center', out.width = '80%'}
knitr::include_graphics("Questionnaire6.png")
```

```{r,echo=FALSE, fig.align='center', out.width = '80%'}
knitr::include_graphics("Questionnaire7.png")
```

```{r,echo=FALSE, fig.align='center', out.width = '80%'}
knitr::include_graphics("Questionnaire8.png")
```

\newpage
# Reference

H. Wickham. ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New 
York, 2016.

Government of Canada, S. C. (2017, February 27). The General Social Survey: An 
overview. Government of Canada, Statistics Canada. Retrieved March 8, 2022, from https://www150.statcan.gc.ca/n1/pub/89f0115x/89f0115x2013001-eng.htm

R Core Team (2021). R: A language and environment for statistical computing. R 
Foundation for Statistical Computing, Vienna, Austria. URL
https://www.R-project.org/.

@@

Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source 
Software, 4(43), 1686, https://doi.org/10.21105/joss.01686
